Deeply Virtual Compton Scattering measurement off bound protons

### 2018-11-05 eg6-letters/incoherent/incoherent_prl.tex
Minor accent issue
the third round comments from the adhoc committee

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
region.  The $t$, transferred momentum squared to the recoil proton, calculated 
from 4-momentum vectors of incoming and outgoing photons, was required to be 
greater than a minimum allowed value at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of 
two photons. At the end of this selection process, about 30k events 
passed all the requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries and independent of $t$ for a bound proton compared to the 
free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated 
from the quark-meson coupling model \cite{Guzey:2008fe}. Our results show that 
an important nuclear effect is missing from the existing models in order to 
explain this strong quenching of the BSA.  More theoretical developments will 
be needed to identify the origin of this quenching, in particular it will be 
key to differenciate initial from final state effects and how they can affect 
the DVCS assymetries.

@@

%conclusion
In summary, we have presented the first BSA measurment associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results were compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
surprising result opens a new avenue for progress in understanding the 
properties of quarks and gluons in the nuclear medium.

@@

\bibitem{Dupre:2015jha} 
  R.~Dupré and S.~Scopetta,
  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass (W$=\sqrt{(q+p)^2}$ assuming the initial proton is at rest) greater than 2 
GeV to avoid the nucleon resonance region.  The $t$, transferred momentum 
squared to the recoil proton, calculated from 4-momentum vectors of incoming 
and outgoing photons, was required to be greater than a minimum allowed value 
at given Q$^2$ and 
W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically use the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
we ensured the exclusivity of the incoherent DVCS events by imposing 
a series of constraints based on the four-momentum conservation 
in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
variables are: the coplanarity angle $\Delta\phi$ between the 
($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
photon and the missing momentum of the $e'p'$ system. The experimental data for 
the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we see no sizeable effect 
that can be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements; their kinematic distributions are shown in 
FIG.~\ref{fig:kin-coverage}.

@@

One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
to see if significant nuclear effects are also visible within the GPD 
framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
protons to that on a free proton target. 
FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
lower asymmetries and independent of $t$ for a bound proton compared to the 
free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated 
from the quark-meson coupling model \cite{Guzey:2008fe}. Our results show that 
an important nuclear effect is missing from the existing models in order to 
explain this strong quenching of the BSA. More theoretical developments will be 
needed to identify the origin of this quenching, in particular it will be key 
to differentiate initial from final state effects and how they can affect the 
DVCS asymmetries.

@@

%conclusion
In summary, we have presented the first BSA measurment associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results were compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using an exciting novel experimental method of 
understanding the properties of bound nucleons directly from the basic degrees 
of freedom of QCD, quarks and gluons.

@@

\bibitem{Dupre:2015jha} 
  R.~Dupr\'e and S.~Scopetta,
  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
